Stochastic Wind Power Forecasting

### 2020-05-31 LaTeX_Code/Paper/paper_1line.tex
abstract

Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and operation scheduling of conventional power plant. We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors. Our SDE framework incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term. We are able to simulate future wind power production paths and to get sharp confidence bands. The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria. We apply the model to historical Uruguayan wind power production data and forecasts on the year 2019.

@@

Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimizaton, model selection.

2020 AMS Subject Classification: 60H10, 62M20.

@@

In this work, we propose a method to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecast technology.

@@

 We conclude that our SDE model, featuring the time-derivative tracking of the forecast prediction function, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently. This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrix.

>>>>

Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price, and operation scheduling of conventional power plants. We propose a data-driven model based on parametric Stochastic Differential Equations (SDEs) to capture the real asymmetric dynamics of wind power forecast errors. Our SDE framework features time-derivative tracking of the forecast, time-varying mean-reversion parameter, and an improved state-dependent diffusion term. The methodology we developed allows the simulation of future wind power production paths and to obtain sharp empirical confidence bands. All the procedure is agnostic of the forecasting technology and enables comparing different forecast providers. We apply the model to historical Uruguayan wind power production data and forecasts during the period April-December 2019.

@@

Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform,

numerical optimizaton, model selection.

2020 AMS Subject Classification: 60H10, 62M20, 65K10.

@@

In this work, we propose a methodology to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecasting technology.

@@

 We conclude that our SDE model, featuring the time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently. This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrix.
